### 2014-12-22 paper_10_intro.tex
note for CMMI and cocomo
add CMMI and Cocomo II and SEMAT details

@@

Quality is tested in \cite{Miguel2014}

See also \cite{Buse2010}.

@@

SEMAT is being dubbed as the ``new software engineering'' \cite{Jacobson2014}.
Three parts to the kernel:
\begin{itemize}
\item Measurement
\item Categorization
\item Competencies
\end{itemize}

The seven dimensions:
\begin{itemize}
\item Opportunity
\item Stakeholders
\item Requirements
\item Software Systems
\item Work
\item Team
\item Way of Working
\end{itemize}

>>>>

\subsection{CMMI}
The Capability Maturity Model Integration (CMMI) is one of the most widely acknowledged models for process 
improvement in software development.  CMMI offers a generic guideline and appraisal program for process 
improvement.  It was created and is administered by the Software Engineering Institute at
Carnegie Mellon University. While the CMMI is not specific to software development,
it is often applied in software development settings.
CMMI certification is required for many United States Government and Department of Defense contracts.

CMMI-Dev is a modification of the CMMI specific to the development activities applied to products
and services \cite{CMMI}.  The practices covered in CMMI-Dev include project management, 
systems engineering, hardware engineering, process management, software engineering, and 
other maintenance processes.  Five maturity levels are specified, and they include the 
existence of a number of process areas.  The 5 maturity levels and the process areas are
specified as follows.

\subsubsection{CMMI MATURITY LEVEL 1 - INITIAL}
    A maturity level 1 organization consists of a adhoc and chaotic processes.  While working
    products are still produced, the results are often over budget and behind schedule.  A level
    1 organization will also have difficulties repeating a process with the same degree of 
    success.  These organizations typically rely on the heroic efforts of certain individuals.

\subsubsection{CMMI MATURITY LEVEL 2 - MANAGED}
    A maturity level 2 organization has a policy for planning and executing processes.  
    The processes are controlled, monitored, reviewed, and enforced.  The practices are even
    maintained in times of stress.  The following process areas should be present at maturity
    level 2.
    \begin{description}
        \item Configuration Management (CM)
        \item Measurement and Analysis (MA)
        \item Project Monitoring and Control (PMC)
        \item Project Planning (PP)
        \item Process and Product Quality Assurance (PPQA)
        \item Requirements Management (REQM)
        \item Supplier Agreement Management (SAM)
    \end{description}

\subsubsection{CMMI MATURITY LEVEL 3 - DEFINED}
    A maturity level 3 organization has well-understood processes that are described in 
    standards, tools, procedures, and methods.  The organization has standard processes
    that are reviewed and improved over time.  The major differentiators between level 2 
    and level 3 is the existence of standards and process descriptions. 
    A level 2 organization will have
    processes that are inconsistent across projects.  A level 3 organization will tailor
    a standard process for each project.  Also, level 3 processes are described with 
    much more rigor.  In addition to the process areas found in level 2, 
    the following process areas should be present at maturity level 3.
    \begin{itemize}
        \item Decision Analysis and Resolution (DAR)
        \item Integrated Project Management (IPM)
        \item Organizational Process Definition (OPD)
        \item Organizational Process Focus (OPF)
        \item Organizational Training (OT)
        \item Product Integration (PI)
        \item Requirements Development (RD)
        \item Risk Management (RSKM)
        \item Technical Solution (TS)
        \item Validation (VAL)
        \item Verification (VER)
    \end{itemize}

\subsubsection{CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED}
    A maturity level 4 organization has quantitative measures for quality and process performance. 
    The measures are based upon customer needs, end users, and process implementers.  The quality
    and process performance are understood mathematically and managed throughout the life of a project.
    Level 4 is characterized by the predictability of the process performance. In addition to
    the process areas found in level 2 and 3, the following additional process areas should be present
    at maturity level 4.
    \begin{itemize}
        \item Organizational Process Performance (OPP)
        \item Quantitative Project Management (QPM)
    \end{itemize}
\subsubsection{CMMI MATURITY LEVEL 5 - OPTIMIZING} 
    The final and pinnacle level of CMMI maturity is level 5.  A maturity level 5 organization
    continually improves processes based upon quantitative measures.  The major distinction from 
    level 4 is the constant focus on improving and managing organizational performance.  A maturity level
    5 organization has well-documented standard processes that are tracked and enforced as well as
    a focus on continual improvement of the processes based upon 
    quantitative measures.  In addition to the process areas of the previous maturity levels, maturity
    level 5 should contain the following process areas.
    \begin{itemize}
        \item Causal Analysis and Resolution (CAR)
        \item Organizational Performance Management (OPM)
    \end{itemize}

        \begin{figure}[here]
            \centering
            \includegraphics[scale=.7]{images/cmmi.png}
            \caption[Characteristics of CMMI]{Characteristics of CMMI, image adapted from  \cite{Godfrey} }
            \label{fig:cmmi}
        \end{figure}

A visual description of the CMMI maturity levels can be seen in Figure \ref{fig:cmmi}.  
While CMMI-Dev does provide an excellent framework for improving a process.  It
is wholely focused on process improvement.  It does not provide guidelines
for evaluating the final product.  
Also, it does not provide a specify mechanism for evaluating
or scoring the progression through the maturity levels.  
An indicator is still needed to quantify the overall performance of an organization, not
just the compliance to standard processes.

\subsection{COCOMO}
    Constructive Cost Model (COCOMO) is a software cost estimation model created
    by Boehm \cite{Boehm1981}.  It combines future project characteristics
    with historical project data to create a regression model to estimate the 
    cost of a software project.  The original version developed in 1981 was
    focused on mainframe and batch processing.  An unpdated version, named
    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
    development practices such as desktop development, off the shelf components,
    and code reuse.  COCOMO provides a nice algorithm for making decisions
    regarding building or buying software products.  It does not provide 
    an algorithms to review past performance of estimates and modify the
    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
    but it only provides an estimate and not an evaluation of the actual
    performance.

@@

\subsubsection{SOFTWARE QUALITY}
Quality is tested in \cite{Miguel2014}

\subsubsection{SOFTWARE ANALYTICS}
See also \cite{Buse2010}.

@@

    Software Engineering Method and Theory (SEMAT) is claiming to be the ``new software engineering'' 
    \cite{Jacobson2014}.  The authors rightfully claim that software engineering lacks
    an underlying theoretical foundation found in other engineering disciplines.  This lack of theory
    has led software engineering to not be engineering, but rather a craft.  The goal of 
    SEMAT is to merge the craftsmanship and engineering to provide a foundation for software
    engineering.  The primary initiative of SEMAT has been the creation of a kernel for 
    software engineering.  The kernel is the minimal set of things common to all software development
    endeavours. The three parts to the kernel are:
    \begin{description}
        \item[Measurement] - There must exist a means to determine the health and progress of an endeavour
        \item[Categorization]-  The activities must progress through categories during an endeavour
        \item[Competencies] - Specific competencies will be required for completing activities
    \end{description}
    The kernel defines alphas, which are seven dimensions with
    specific states for measuring progress. 
    The seven dimensions are: 
    \begin{enumerate}
        \item Opportunity
        \item Stakeholders
        \item Requirements
        \item Software Systems
        \item Work
        \item Team
        \item Way of Working
    \end{enumerate}

    Although SEMAT is very promising, the development is not yet complete.  Adoption is
    limited so the technique has not been validated on many
    actual software engineering endeavours.  Although SEMAT does include a part for
    measurement of progress, it does not specify how the measurement is to be 
    performed.
